---
title: "solar panel data analysis"
output:
  html_document:
    number_sections: true
    fig_caption: true
    toc: true
    fig_width: 5
    fig_height: 4
    theme: cosmo
    highlight: tango
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.align = "center")
```

# Preparations (준비작업) {.tabset .tabset-fade}

## Libraries

```{r load_lib, message=FALSE, warning=FALSE, results='hide'}
library(tidyverse)
library(tidymodels)
library(lubridate)
library(data.table)
library(skimr)
library(tibble)
library(tibbletime)
library(timetk)
library(imputeTS)
library(anomalize)
library(forecast)
library(GGally)
library(modeltime)
library(gt)
library(timetk)
library(lubridate)
library(janitor)
library(tidyquant)
library(sknifedatar)

# Visualization
library(ggthemes)
library(ggsci)
library(viridis)
library(ggExtra)


theme_set(theme_bw())
```

## Data load

```{r}
file_path <- "./data/"
files <- list.files(file_path)
files
```

```{r, message=FALSE}
rdata1 <- fread(file.path(file_path, "rdata1.csv"))
rdata2 <- fread(file.path(file_path, "rdata2.csv"))

```

# Data overview (데이터 기본정보) {.tabset .tabset-fade}

## data

```{r}
glimpse(rdata1)
glimpse(rdata2)
skim(rdata1)
skim(rdata2)

```

# 데이터 전처리 {.tabset .tabset-fade}


```{r}
rdata2 %>% 
    mutate(time = ymd_hms(time)) %>% 
    filter(between(time, ymd('2018-03-01'), ymd('2021-01-31'))) -> rdata2
  
rdata2 %>% 
  summarise(across(.fns = ~sum(is.na(.))/length(.)))

```


# data split 

```{r}
splits <- time_series_split(rdata2, assess = "1 month", cumulative = TRUE)

splits %>%
  tk_time_series_cv_plan() %>%
  plot_time_series_cv_plan(time, ulsan, .interactive = FALSE)


train_df <- training(splits)
test_df <- testing(splits)
```

# Modeling


```{r}
# ARIMA Boost
model_fit_arima_boost <- modeltime::arima_boost() %>%
    parsnip::set_engine("auto_arima_xgboost") 


```


# Model time table 

modeltime_table에 피팅한 모델을 추가함. 
modeltime_table은 각 모델이 재대로 적합되었는지 확인하고, 이후 예측 워크플로우를 위해서 modeltime_table 구조를 이용함 

```{r}
model_tbl <- modeltime::modeltime_table(
    model_fit_ets,
    model_fit_arima,
    model_fit_arima_boost,
    model_fit_prophet,
    model_fit_prophet_boost)

model_tbl
```

# calibration 

이전에 만든 modeltime_table을 test 데이터에 적합시켜서 보정을 함

* Calibration is how confidence intervals and accuracy metrics are determined
* Calibration Data is simply forecasting predictions and residuals that are calculated from out-of-sample data.
* After calibrating, the calibration data follows the data through the
forecasting workflow.

```{r}
calibration_tbl <- model_tbl %>%
    modeltime::modeltime_calibrate(testing(splits))  
```


```{r}
calibration_tbl %>%
    modeltime::modeltime_accuracy() %>%   
    flextable::flextable() %>% 
    flextable::bold(part = "header") %>% 
    flextable::bg(bg = "#D3D3D3", part = "header") %>% 
    flextable::autofit()
```

# visualization the forecast test 

```{r}
calibration_tbl %>%
    modeltime::modeltime_forecast(new_data = testing(splits), 
                                  actual_data = ulsan,
                                  conf_interval = 0.90) %>%
    modeltime::plot_modeltime_forecast(.legend_show = TRUE, 
                                       .legend_max_width = 20)
```


# refit
```{r}
refit_tbl <- calibration_tbl %>%
    modeltime::modeltime_refit(data = ulsan)
```



# forecast 
```{r}
forecast_tbl <- refit_tbl %>%
    modeltime::modeltime_forecast(
        h = "1 month",
        actual_data = ulsan,
        conf_interval = 0.90
    ) 

forecast_tbl %>%
    modeltime::plot_modeltime_forecast(.interactive = TRUE,
                                       .legend_max_width = 20)
```


